# **Tweet Scrape**

In order to get the Tweets I will first need to load the packages `tidyverse` and `rtweet`.

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(rtweet)
```

Next I can authenticate my Twitter developer account.

```{r warning=FALSE, message=FALSE}
auth_setup_default()
auth_has_default()
```

## Rocket League Tweets

Finally I will then search and scrape tweets that contain 'rocket league', I am doing 1000 Tweets at a time, that do not include Retweets and are in English.

```{r eval=FALSE}
df <- search_tweets("rocket league", n = 1000, include_rts = FALSE, lang = "en")
```

### Divide Tweets Data

Now I will clean up the dataset into two more manageable tables that will be imported in into my `postgreSQL` database.

```{r eval=FALSE}
df1 <- df %>%
  select(id_str, retweet_count, favorite_count,  created_at)

df2 <- df %>%
  select(id_str, full_text, display_text_range, text)
```

### Export Data

After creating the two tables, I will export them in `.csv` format. I will then get on pgadmin4 and import the `.csv`'s into the database.

```{r eval=FALSE}
write_csv(df1, "tweet_data.csv", col_names = FALSE)
write_csv(df2, "tweet_text.csv", col_names = FALSE)
```

## Pokémon Go Tweets

```{r eval=FALSE}
pdf <- search_tweets("pokemon go", n = 1000, include_rts = FALSE, lang = "en")
```

### Divide and Export Tweets Data

```{r eval=FALSE}
pdf1 <- pdf %>%
  select(id_str, retweet_count, favorite_count,  created_at)

pdf2 <- pdf %>%
  select(id_str, full_text, display_text_range, text)
```

### Export Data

```{r eval=FALSE}
write_csv(df1, "tweet_data.csv", col_names = FALSE)
write_csv(df2, "tweet_text.csv", col_names = FALSE)
```
